---
title: "Knowledge imbalance in Palaeontology"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    # source: embed
    css: assets/style.css
#    logo: favicon_48x48.png
#    favicon: favicon_48x48.png
    navbar:
      - { title: "Back to Homepage", icon: "fa-home", href: "https://paleoscientometrics.github.io/", align: right }
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)

```

```{r data, include=FALSE}
pbdb <- readRDS(file.path("data", "pbdb.rds"))
pal <- c("#f0ffe9", "#ffe599", "#bbe487", "#4e9755", "#173109")
```

### Based on data in the **Paleobiology Database**, the majority of fossil collections are located in **North America** and **Europe**. A small portion also comes from the East Asian region. {data-commentary-width=400}

```{r sampling-gauge}
source("scripts/01-bubble_map.R")

fig_fn
```

***

<center>![](assets/gauge.svg){#id .class width=400px} </center>

We only focus on publications published betweeen 1990 - 2020.

***
#### Proportions of fossil collections in:

- **Northern America:** `r round(sum(colls[colls$region == "Northern America",]$n)/sum(colls$n)*100,2)` %

- **Northern & Western Europe:** `r round(sum(colls[colls$region %in% c("Western Europe", "Northern Europe"),]$n)/sum(colls$n)*100,2)` %

- **East Asia:** `r round(sum(colls[colls$region == "Eastern Asia",]$n)/sum(colls$n)*100, 2)` %

<p><span style="float:right;">*Last updated 31 January 2021*.</span></p>

### The regions where the most sampled collections are, also tend to be where **high income** countries with higher Gross Domestic Product (GDP) and available research funding are located. {data-commentary-width=600}

```{r circle-packing, cached=TRUE}
source("scripts/02-sunburst.R")

fig_sb
```

***

<h4> ![](assets/iconmonstr-arrow-72.svg){#id .class width=24px}  Proportion of fossil collections per region, income class and countries </h4>
*Hover over the sections to see the details.*

The **darker regions** represents the regions, income classes or countries with the the **highest number of fossil collections**.

In general, regions like **Europe** and **Americas (mostly Northern America)** have the most number of fossil collections in their regions. Lower income countries, especially most of *Africa* and parts of *Asia* tend to have a lower number of fossil collections in the region.

***
<div style="max-height:300px">

```{r, gdp-research}
source("scripts/03-gdp_funding.R")
fig
```
</div>

### Most **researchers** reporting these fossil collections were also based at institutions in **high income countries**, leading to a greater imbalance to who **gets to do research and where**. {data-commentary-width=400}

```{r researchers_country}
source("scripts/04-researchers.R")

fig_fn2
```

***

High income countries in general also **produce more researchers** in average. With the availability of more **research funding**, these researchers have **higher mobility** as to where they can go to conduct fieldwork as compared to other income groups.

This is especially true for Northern America and most of Europe, which shows a major concentration of the source of publications in the field of palaeontology.

***

```{r number-of-researchers}
fig2
```

### Most palaeontological publications, as in the rest of academia, were in English, with a smaller portion in German and French. {data-commentary-width=600}

<div style="max-height:300px">
```{r language}
source("scripts/05-language.R")

widg
```
</div>

***
Things will go here
