---
title: "Knowledge imbalance in Palaeontology"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    vertical_layout: fill
    social: menu
    # source: embed
    css: assets/style.css
#    logo: favicon_48x48.png
#    favicon: favicon_48x48.png
    navbar:
      - { title: "Back to Homepage", icon: "fa-home", href: "https://paleoscientometrics.github.io/", align: right }
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)

```

```{r data, include=FALSE}
pbdb <- readRDS(file.path("data", "pbdb.rds"))
pal <- c("#f0ffe9", "#ffe599", "#bbe487", "#4e9755", "#173109")
```

### Based on data in the **Paleobiology Database**, the majority of fossil collections are located in **North America** and **Europe**. A small portion also comes from the East Asian region. {data-commentary-width=400}

```{r sampling-gauge}
source("scripts/01-bubble_map.R")

fig_fn
```

***

<center>![](assets/gauge.svg){#id .class width=400px} </center>

We only focus on publications published betweeen 1990 - 2020.

***
#### Proportions of fossil collections in:

- **Northern America:** `r round(sum(colls[colls$region == "Northern America",]$n)/sum(colls$n)*100,2)` %

- **Northern & Western Europe:** `r round(sum(colls[colls$region %in% c("Western Europe", "Northern Europe"),]$n)/sum(colls$n)*100,2)` %

- **East Asia:** `r round(sum(colls[colls$region == "Eastern Asia",]$n)/sum(colls$n)*100, 2)` %

<p><span style="float:right;">*Last updated 31 January 2021*.</span></p>

### The regions where the most sampled collections are, also tend to be where **high income** countries with higher Gross Domestic Product (GDP) and available research funding are located. {data-commentary-width=600}

```{r circle-packing, cached=TRUE}
source("scripts/02-sunburst.R")

fig_sb
```

***

<h4> ![](assets/iconmonstr-arrow-72.svg){#id .class width=24px}  Proportion of fossil collections per region, income class and countries </h4>
*Hover over the sections to see the details.*

The **darker regions** represents the regions, income classes or countries with the the **highest number of fossil collections**.

In general, regions like **Europe** and **Americas (mostly Northern America)** have the most number of fossil collections in their regions. Lower income countries, especially most of *Africa* and parts of *Asia* tend to have a lower number of fossil collections in the region.

***
<div style="max-height:300px">

```{r, gdp-research}
source("scripts/03-gdp_funding.R")
fig
```
</div>

### Most **researchers** reporting these fossil collections were also based at institutions in **high income countries**, leading to a greater imbalance to who **gets to do research and where**. {data-commentary-width=400}

```{r researchers_country}
source("scripts/04-researchers.R")

fig_fn2
```

***

High income countries in general also **produce more researchers** in average. With the availability of more **research funding**, these researchers have **higher mobility** as to where they can go to conduct fieldwork as compared to other income groups.

This is especially true for Northern America and most of Europe, which shows a major concentration of the source of publications in the field of palaeontology.

***

```{r number-of-researchers}
fig2
```

### Most palaeontological **publications**, as in the rest of academia, were **in English**, with a smaller portion in Spanish, German and French, showing clear **evidence of linguistic bias**. {data-commentary-width=600}

```{r language}
source("scripts/05-language.R")

widg
```

***
Through centuries of colonialism, neocolonialism, Cold War expansionism, and, most recently, globalization, English has become the **world's most dominant language** in academia (as well as in other sectors). The  monopoly  of the English-language  in scientific journals  means  that scholarly interests  are **controlled by a specific group** of researchers. This is bias clearly exists in our data, which is mostly curated by researchers from English-speaking countries or countries with high English proficiency.

#### **Did you know that countries with higher English proficiencies tend to have better economies?**

The interaction between English proficiency and economic performance is a virtuous cycle, with improving English skills driving up performance, which in turn give governments more funds to invest in language training. Countries with higher English proficiency spend a significantly larger share of their GDP on research and also tend to have more researchers per capita.

<div style="max-height:300px">


```{r language-2}
fig_eng
```
</div>

### But **research output** is not only linked to **economic growth** but also other **social dimensions** such as life expectancy, education and the standard of living as well as political stability. {data-commentary-width=500}

```{r complex-graph}
source("scripts/06-HDI.R")

fig_hdi
```

*** 

#### How to read this graph

```{r how-to, fig.width=5, fig.height=4}
p <- ggplot(data.frame(x=c(0,0.5,0.85), y=c(0,0,0), size=c(3,2,1), lang=c(3,1,2)), 
	   aes(x=x, y=y, size=size, fill=size, color=as.factor(lang))
	   ) +
	geom_point(alpha=0.7, shape=21, stroke=2) +
	scale_size(range=c(10,30))+
	scale_fill_gradient(low=pal[1], high=pal[4]) +
	scale_color_manual(values=c("grey60", "grey30", "grey10"), breaks=c(1,2,3)) +
	coord_cartesian(ylim=c(-0.1,0.1), xlim=c(-0.2,1.3)) +
	theme_void() +
	theme(legend.position ="none")
p <- p + annotate("segment", x=-0.15, xend = 0.85, y=-0.04, yend=-0.04, size=1,
			 arrow=arrow(type="closed", length=unit(0.15, "inches")), color="darkgrey") +
	annotate("text", x=0.35, y=-0.05, size=3, fontface=3, color="grey20",
			 label="Decreasing size represents \ndecreasing number of collections")
p <- p + annotate("segment", x=c(0, 0.5), xend=c(0.15, 0.35), 
			 y=c(0.03, 0.025), yend=0.06, size=1, color="grey50",
			 arrow=arrow(type="closed", length=unit(0.15, "inches"), ends="first")) +
	annotate("text", x=0.25, y=0.08, size=3, fontface=3, color="grey20",
			 label="The lighter the line colours, \nthe lower the English proficiency \nof the population of the country")
p <- p + annotate("segment", x=0.85, xend=0.95, 
			 y=0, yend=0.03, color="grey50", size=1,
			 arrow=arrow(type="closed", length=unit(0.08, "inches"), ends="first")) +
	annotate("text", x=0.8, y=0.05, size=3, fontface=3, color="grey20", hjust=0,
			 label="The colour of the circle\nshows the GDP per capita.\nThe darker the circle, \nthe higher the GDP")

p + annotate("text", x=-0.3, y=-0.08, size=3, fontface=2, color="grey20", hjust=0,
			  label="The x-axis shows increasing human development and the y-axis \nincrease peace in a country.") +
	annotate("text", x=-0.3, y=-0.1, size=3, fontface=3, color="grey20", hjust=0,
			 label="Hover over the points of the graph for more details.")

```

The **Human Development Index (HDI)**  is a statistic composite index of life expectancy, education (literacy rate, gross enrollment ratio at different levels and net attendance ratio), and per capita income indicators. A country scores a higher HDI when the lifespan is higher, the education level is higher, and the gross national income GNI (PPP) per capita is higher. 

The **Global Peace Index (GPI)** measures the relative position of nations' and regions' peacefulness.The lower the number, the more peaceful the country.
