---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    source: embed
    theme: cosmo
#    logo: favicon_48x48.png
#    favicon: favicon_48x48.png
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)

```

```{r data, include=FALSE}
pbdb <- readRDS(file.path("data", "pbdb.rds"))
pal <- c("#f0ffe9", "#ffe599", "#bbe487", "#4e9755", "#173109")
```

### Fossil sampling is concentrated mainly in the US and Europe, followed by East Asia

```{r sampling}
source("scripts/01-bubble_map.R")

fig
```

***

https://rstudio.github.io/leaflet/

- Interactive panning/zooming

- Compose maps using arbitrary combinations of map tiles, markers, polygons, lines, popups, and GeoJSON.

- Create maps right from the R console or RStudio

- Embed maps in knitr/R Markdown documents and Shiny apps

- Easily render Spatial objects from the sp package, or data frames with latitude/longitude columns

- Use map bounds and mouse events to drive Shiny logic


### Chart B

```{r}

```

### Chart C

```{r}

```

